Parameter Estimation for the CES Model

### 2013-07-19 CES.Rnw
Added a suggestion for how we could fit CES with constraints.

>>>>

It is possible to set $\rho_1$ to a specific number 
(in this case, we could choose $\rho_1 = -0.99$; $-1.0$ would 
blow up)
and have \texttt{cesEst} fit the remaining parameters.
If we went this route, we would be going in a direction that
is similar to our approach to the constraints
on the Cobb-Douglas model, wherein we fit the unconstrained 
model first. If the unconstrained fit violates any constraints, 
we set the offending parameter at the constraint 
and re-fit the remaining the parameters.
